How Kids Code and How We Know:\\An Exploratory Study on the Scratch Repository

### 2016-06-29 Paper/paper.tex
Included the bibliography in the tex file

\bibliographystyle{abbrv}
\bibliography{zotero}
\end{document}

>>>>

\begin{thebibliography}{10}

	\bibitem{alves_deriving_2010}
	T.~L. Alves, C.~Ypma, and J.~Visser.
	\newblock Deriving metric thresholds from benchmark data.
	\newblock In {\em 26th {IEEE} {International} {Conference} on {Software}
		{Maintenance} ({ICSM} 2010)}, pages 1--10. IEEE Computer Society, 2010.

	\bibitem{boe_hairball:_2013}
	B.~Boe, C.~Hill, M.~Len, G.~Dreschler, P.~Conrad, and D.~Franklin.
	\newblock Hairball: {Lint}-inspired {Static} {Analysis} of {Scratch}
	{Projects}.
	\newblock In {\em Proceeding of the 44th {ACM} {Technical} {Symposium} on
		{Computer} {Science} {Education}}, {SIGCSE} '13, pages 215--220, New York,
	NY, USA, 2013. ACM.

	\bibitem{brennan_creative_2014}
	K.~Brennan, C.~Balch, and M.~Chung.
	\newblock {\em {Creative} {Computing}}.
	\newblock Harvard Graduate School of Education, 2014.

	\bibitem{conway_alice:_1994}
	M.~Conway, R.~Pausch, R.~Gossweiler, and T.~Burnette.
	\newblock Alice: {A} {Rapid} {Prototyping} {System} for {Building} {Virtual}
	{Environments}.
	\newblock In {\em Conference {Companion} on {Human} {Factors} in {Computing}
		{Systems}}, {CHI} '94, pages 295--296, New York, NY, USA, 1994. ACM.

	\bibitem{cooper_teaching_2003}
	S.~Cooper, W.~Dann, and R.~Pausch.
	\newblock Teaching {Objects}-first in {Introductory} {Computer} {Science}.
	\newblock In {\em Proceedings of the 34th {SIGCSE} {Technical} {Symposium} on
		{Computer} {Science} {Education}}, {SIGCSE} '03, pages 191--195, New York,
	NY, USA, 2003. ACM.

	\bibitem{Dasgupta_2016}
	S.~Dasgupta, W.~Hale, A.~Monroy-Hern\'{a}ndez, and B.~M. Hill.
	\newblock Remixing as a pathway to computational thinking.
	\newblock In {\em Proceedings of the 19th ACM Conference on Computer-Supported
		Cooperative Work \& Social Computing}, CSCW '16, pages 1438--1449, New York,
	NY, USA, 2016. ACM.

	\bibitem{fields_2014}
	D.~A. Fields, M.~Giang, and Y.~Kafai.
	\newblock Programming in the wild: Trends in youth computational participation
	in the online scratch community.
	\newblock In {\em Proceedings of the 9th Workshop in Primary and Secondary
		Computing Education}, WiPSCE '14, pages 2--11, New York, NY, USA, 2014. ACM.

	\bibitem{fowler_refactoring:_1999}
	M.~Fowler.
	\newblock {\em Refactoring: improving the design of existing code}.
	\newblock Addison-Wesley Longman Publishing Co., Inc., Boston, MA, USA, 1999.

	\bibitem{e._glinert_towards_1986}
	E.~Glinert.
	\newblock {Towards} "{Second} {Generation}" {Interactive}, {Graphical}
	{Programming} {Environments}.
	\newblock In {\em Proceedings of the {IEEE} {Workshop} on {Visual}
		{Languages}}, pages 61---70, 1986.

	\bibitem{hermans_2016}
	F.~Hermans and E.~Aivaloglou.
	\newblock Do code smells hamper novice programming?
	\newblock In {\em Proceedings of the International Conference on Program
		Comprehension}, 2016.
	\newblock to appear.

	\bibitem{hermans2015detecting}
	F.~Hermans, M.~Pinzger, and A.~van Deursen.
	\newblock Detecting and refactoring code smells in spreadsheet formulas.
	\newblock {\em Empirical Software Engineering}, 20(2):549--575, 2015.

	\bibitem{Maloney_2008}
	J.~H. Maloney, K.~Peppler, Y.~Kafai, M.~Resnick, and N.~Rusk.
	\newblock Programming by choice: Urban youth learning programming with scratch.
	\newblock In {\em Proceedings of the 39th SIGCSE Technical Symposium on
		Computer Science Education}, SIGCSE '08, pages 367--371, New York, NY, USA,
	2008. ACM.

	\bibitem{mcCabe76}
	T.~J. McCabe.
	\newblock A complexity measure.
	\newblock {\em {IEEE} Trans. Software Eng.}, 2(4):308--320, 1976.

	\bibitem{Meerbaum_habits_2011}
	O.~Meerbaum-Salant, M.~Armoni, and M.~Ben-Ari.
	\newblock Habits of programming in scratch.
	\newblock In {\em Proceedings of the 16th Annual Joint Conference on Innovation
		and Technology in Computer Science Education}, ITiCSE '11, pages 168--172,
	New York, NY, USA, 2011. ACM.

	\bibitem{meerbaum-salant_learning_2010}
	O.~Meerbaum-Salant, M.~Armoni, and M.~M. Ben-Ari.
	\newblock Learning {Computer} {Science} {Concepts} with {Scratch}.
	\newblock In {\em Proceedings of the {Sixth} {International} {Workshop} on
		{Computing} {Education} {Research}}, {ICER} '10, pages 69--76, New York, NY,
	USA, 2010. ACM.

	\bibitem{moreno_automatic_2014}
	J.~Moreno and G.~Robles.
	\newblock Automatic detection of bad programming habits in scratch: {A}
	preliminary study.
	\newblock In {\em 2014 {IEEE} {Frontiers} in {Education} {Conference} ({FIE})},
	pages 1--4, Oct. 2014.

	\bibitem{moreno-leon_dr._2015}
	J.~Moreno-Le{\'o}n, G.~Robles, and M.~Rom{\'a}n-Gonz{\'a}lez.
	\newblock Dr. {Scratch}: {Automatic} {Analysis} of {Scratch} {Projects} to
	{Assess} and {Foster} {Computational} {Thinking}.
	\newblock {\em RED : Revista de Educaci{\'o}n a Distancia}, (46):1--23, Jan.
	2015.

	\bibitem{b._moskal_evaluating_2005}
	B.~Moskal, S.~Cooper, and D.~Lurie.
	\newblock Evaluating the {Effectiveness} of a {New} {Instructional} {Approach}.
	\newblock In {\em Proceedings of the {SIGCSE} technical symposium on {Computer}
		science education}, 2005.

	\bibitem{price_comparing_2015}
	T.~W. Price and T.~Barnes.
	\newblock Comparing {Textual} and {Block} {Interfaces} in a {Novice}
	{Programming} {Environment}.
	\newblock In {\em Proceedings of the {Eleventh} {Annual} {International}
		{Conference} on {International} {Computing} {Education} {Research}}, {ICER}
	'15, pages 91--99, New York, NY, USA, 2015. ACM.

	\bibitem{resnick_scratch:_2009}
	M.~Resnick, J.~Maloney, A.~Monroy-Hernández, N.~Rusk, E.~Eastmond, K.~Brennan,
	A.~Millner, E.~Rosenbaum, J.~Silver, B.~Silverman, and Y.~Kafai.
	\newblock Scratch: {Programming} for {All}.
	\newblock {\em Commun. ACM}, 52(11):60--67, Nov. 2009.

	\bibitem{seiter_2013}
	L.~Seiter and B.~Foreman.
	\newblock Modeling the learning progressions of computational thinking of
	primary grade students.
	\newblock In {\em Proceedings of the Ninth Annual International ACM Conference
		on International Computing Education Research}, ICER '13, pages 59--66, New
	York, NY, USA, 2013. ACM.

	\bibitem{wilson_evaluation_2012}
	A.~Wilson, T.~Hainey, and T.~Connolly.
	\newblock Evaluation of computer games developed by primary school children to
	gauge understanding of programming concepts.
	\newblock In {\em European Conference on Games Based Learning}, page 549.
	Academic Conferences International Limited, 2012.

	\bibitem{wolber_app_2011}
	D.~Wolber, H.~Abelson, E.~Spertus, and L.~Looney.
	\newblock {\em App {Inventor}: {Create} {Your} {Own} {Android} {Apps}}.
	\newblock O'Reilly Media, Sebastopol, Calif, 1 edition edition, May 2011.

	\bibitem{yang_2015}
	S.~Yang, C.~Domeniconi, M.~Revelle, M.~Sweeney, B.~U. Gelman, C.~Beckley, and
	A.~Johri.
	\newblock Uncovering trajectories of informal learning in large online
	communities of creators.
	\newblock In {\em Proceedings of the Second (2015) ACM Conference on Learning @
		Scale}, L@S '15, pages 131--140, New York, NY, USA, 2015. ACM.

\end{thebibliography}

\end{document}
